---


Test {.storyboard}
=========================================

<!--create a data frame giving the hierarchical structure of your individuals

```{r}
set.seed(1234)
d1 <- data.frame(from="origin", to=paste("group", seq(1,10), sep=""))
d2 <- data.frame(from=rep(d1$to, each=10), to=paste("subgroup", seq(1,100), sep="_"))
edges <- rbind(d1, d2)
```

<!--create a dataframe with connection between leaves (individuals)

```{r}
all_leaves <- paste("subgroup", seq(1,100), sep="_")
connect <- rbind( 
  data.frame( from=sample(all_leaves, 100, replace=T) , to=sample(all_leaves, 100, replace=T)), 
  data.frame( from=sample(head(all_leaves), 30, replace=T) , to=sample( tail(all_leaves), 30, replace=T)), 
  data.frame( from=sample(all_leaves[25:30], 30, replace=T) , to=sample( all_leaves[55:60], 30, replace=T)), 
  data.frame( from=sample(all_leaves[75:80], 30, replace=T) , to=sample( all_leaves[55:60], 30, replace=T)) )
connect$value <- runif(nrow(connect))
```

<!--create a vertices data.frame. One line per object of our hierarchy
```{r}
vertices  <-  data.frame(
  name = unique(c(as.character(edges$from), as.character(edges$to))) , 
  value = runif(111)
) 
```

<!--# Let's add a column with the group of each name. It will be useful later to color points
```{r}
vertices$group  <-  edges$from[ match( vertices$name, edges$to ) ]
```


<!--Let's add information concerning the label we are going to add: angle, horizontal adjustement and potential flip
#calculate the ANGLE of the labels

```{r}
vertices$id <- NA
myleaves <- which(is.na( match(vertices$name, edges$from) ))
nleaves <- length(myleaves)
vertices$id[ myleaves ] <- seq(1:nleaves)
vertices$angle <- 90 - 360 * vertices$id / nleaves
 
# calculate the alignment of labels: right or left
# If I am on the left part of the plot, my labels have currently an angle < -90
vertices$hjust <- ifelse( vertices$angle < -90, 1, 0)
 
# flip angle BY to make them readable
vertices$angle <- ifelse(vertices$angle < -90, vertices$angle+180, vertices$angle)
```

<!--- create a graph object 
```{r}
mygraph <- igraph::graph_from_data_frame( edges, vertices=vertices )
```
<!--- The connection object must refer to the ids of the leaves: 

```{r}
from  <-  match( connect$from, vertices$name)
to  <-  match( connect$to, vertices$name)
```

<!--- Basic usual argument
```{r}
ggraph(mygraph, layout = 'dendrogram', circular = TRUE) + 
  geom_conn_bundle(data = get_con(from = from, to = to), alpha=0.2, width=0.9, aes(colour=..index..)) +
  scale_edge_colour_distiller(palette = "RdPu") +
  
  geom_node_text(aes(x = x*1.15, y=y*1.15, filter = leaf, label=name, angle = angle, hjust=hjust, colour=group), size=2, alpha=1) +
  
  geom_node_point(aes(filter = leaf, x = x*1.07, y=y*1.07, colour=group, size=value, alpha=0.2)) +
  scale_colour_manual(values= rep( brewer.pal(9,"Paired") , 30)) +
  scale_size_continuous( range = c(0.1,10) ) +
  
  theme_void() +
  theme(
    legend.position="none",
    plot.margin=unit(c(0,0,0,0),"cm"),
  ) +
  expand_limits(x = c(-1.3, 1.3), y = c(-1.3, 1.3))
```


Test2 {.storyboard}
=========================================
```{r}
dataUU <- scores

connect <- dataUU %>% 
  gather(key="to", value="value", -1) %>%
  mutate(to = gsub("\\.", " ",to)) %>%
  na.omit() 


c( as.character(connect$from), as.character(connect$to)) %>%
  as.tibble() %>%
  group_by(value) %>%
  summarize(n=n()) -> valence
colnames(valence ) <- c("name", "n")
#dim(coauth)


mygraph <- graph_from_data_frame( connect, vertices = coauth, directed = FALSE )

com <- walktrap.community(mygraph)
#max(com$membership)

coauth <- coauth %>% 
  mutate( grp = com$membership) %>%
  arrange(grp) %>%
  mutate(name=factor(name, name))


coauth <- coauth %>% 
  filter(grp<16)

connect <- connect %>%
  filter(from %in% coauth$name) %>%
  filter(to %in% coauth$name)


mygraph <- graph_from_data_frame( connect, vertices = coauth, directed = FALSE )


mycolor <- colormap(colormap=colormaps$viridis, nshades=max(coauth$grp))
mycolor <- sample(mycolor, length(mycolor))


ggraph(mygraph, layout="linear") + 
  geom_edge_arc(edge_colour="black", edge_alpha=0.2, edge_width=0.3, fold=TRUE) +
  geom_node_point(aes(size=n, color=as.factor(grp), fill=grp), alpha=0.5) +
  scale_size_continuous(range=c(0.5,8)) +
  scale_color_manual(values=mycolor) +
  geom_node_text(aes(label=name), angle=65, hjust=1, nudge_y = -1.1, size=2.3) +
  theme_void() +
  theme(
    legend.position="none",
    plot.margin=unit(c(0,0,0.4,0), "null"),
    panel.spacing=unit(c(0,0,3.4,0), "null")
  ) +
  expand_limits(x = c(-1.2, 1.2), y = c(-5.6, 1.2)) 
```





 

Tempo {.storyboard}
=========================================

<!-- 
### Tempogram


```{r, include = FALSE}
wakanda <-
  get_tidy_audio_analysis("0w7yUSxpQV3a3HqlprOQUs") %>%
  select(segments) %>%
  unnest(segments)


```



```{r include = FALSE}
p1 <- wakanda %>%
  mutate(loudness_max_time = start + loudness_max_time) %>%
  arrange(loudness_max_time) %>%
  mutate(delta_loudness = loudness_max - lag(loudness_max)) %>%
  ggplot(aes(x = loudness_max_time, y = pmax(0, delta_loudness))) +
  geom_line() +
  xlim(0, 140) +
  theme_minimal() +
  labs(x = "Time (s)", y = "Novelty")

```


```{r include = FALSE}
p2 <- wakanda %>%
  mutate(pitches = map(pitches, compmus_normalise, "clr")) %>%
  arrange(start) %>%
  mutate(pitches = map2(pitches, lag(pitches), `-`)) %>%
  slice(-1) %>%
  compmus_gather_chroma() %>%
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = pmax(0, value)
    )
  ) +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  xlim(0, 30) +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  theme_classic()
```


```{r include = TRUE}
wakanda2 <- get_tidy_audio_analysis("0w7yUSxpQV3a3HqlprOQUs")
```


```{r include = FALSE}


p3 <- wakanda2 %>%
  tempogram(window_size = 8, hop_size = 1, cyclic = FALSE) %>%
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()


```


```{r include = TRUE}
a <- p1
b <- p2
c <- p3

grid.newpage()
pushViewport(viewport(layout = grid.layout(2, 2)))
vplayout <- function(x, y) viewport(layout.pos.row = x, layout.pos.col = y)
print(b, vp = vplayout(1, 1))
print(c, vp = vplayout(1, 2))
print(a, vp = vplayout(2, 1:2))

```

```{r include = FALSE}
plots <- list(p1, p2)
```

```{r}

```

***


For tempo i've chosen the song Kilmonger from the Black Panther's score. I think this was an interesting song to analyse because of its different layers it contains. In the beginning you can hear a flute, which represents kilmonger's African background. The flute is pitched down and escalates into chaos. The next layer are the strings and they go up in arpeggios. These escalate and grow bigger. Then suddenly the music cuts out and 808 drums start to kick. It feels dangerous and they come out of nowhere. They have a really low bass and sound like heartbeats. The last layer is the trap beat, representing him coming from Oakland. 

'' note / 
I want to show these layers with lines in the plots and be more specific about what happens with the changes in tempo.  

---> 

<!-- Chroma Plot --> 

circlize {.storyboard}
=========================================

###

```{r}
data <- read.lolli
```

```{r}

data <- as.matrix(data)

```

```{r}
chordDiagram(data)
```



Test {.storyboard}
=========================================

<!--create a data frame giving the hierarchical structure of your individuals

```{r}
set.seed(1234)
d1 <- data.frame(from="origin", to=paste("group", seq(1,10), sep=""))
d2 <- data.frame(from=rep(d1$to, each=10), to=paste("subgroup", seq(1,100), sep="_"))
edges <- rbind(d1, d2)
```

<!--create a dataframe with connection between leaves (individuals)

```{r}
all_leaves <- paste("subgroup", seq(1,100), sep="_")
connect <- rbind( 
  data.frame( from=sample(all_leaves, 100, replace=T) , to=sample(all_leaves, 100, replace=T)), 
  data.frame( from=sample(head(all_leaves), 30, replace=T) , to=sample( tail(all_leaves), 30, replace=T)), 
  data.frame( from=sample(all_leaves[25:30], 30, replace=T) , to=sample( all_leaves[55:60], 30, replace=T)), 
  data.frame( from=sample(all_leaves[75:80], 30, replace=T) , to=sample( all_leaves[55:60], 30, replace=T)) )
connect$value <- runif(nrow(connect))
```

<!--create a vertices data.frame. One line per object of our hierarchy
```{r}
vertices  <-  data.frame(
  name = unique(c(as.character(edges$from), as.character(edges$to))) , 
  value = runif(111)
) 
```

<!--# Let's add a column with the group of each name. It will be useful later to color points
```{r}
vertices$group  <-  edges$from[ match( vertices$name, edges$to ) ]
```


<!--Let's add information concerning the label we are going to add: angle, horizontal adjustement and potential flip
#calculate the ANGLE of the labels

```{r}
vertices$id <- NA
myleaves <- which(is.na( match(vertices$name, edges$from) ))
nleaves <- length(myleaves)
vertices$id[ myleaves ] <- seq(1:nleaves)
vertices$angle <- 90 - 360 * vertices$id / nleaves
 
# calculate the alignment of labels: right or left
# If I am on the left part of the plot, my labels have currently an angle < -90
vertices$hjust <- ifelse( vertices$angle < -90, 1, 0)
 
# flip angle BY to make them readable
vertices$angle <- ifelse(vertices$angle < -90, vertices$angle+180, vertices$angle)
```

<!--- create a graph object 
```{r}
mygraph <- igraph::graph_from_data_frame( edges, vertices=vertices )
```
<!--- The connection object must refer to the ids of the leaves: 

```{r}
from  <-  match( connect$from, vertices$name)
to  <-  match( connect$to, vertices$name)
```

<!--- Basic usual argument
```{r}
ggraph(mygraph, layout = 'dendrogram', circular = TRUE) + 
  geom_conn_bundle(data = get_con(from = from, to = to), alpha=0.2, width=0.9, aes(colour=..index..)) +
  scale_edge_colour_distiller(palette = "RdPu") +
  
  geom_node_text(aes(x = x*1.15, y=y*1.15, filter = leaf, label=name, angle = angle, hjust=hjust, colour=group), size=2, alpha=1) +
  
  geom_node_point(aes(filter = leaf, x = x*1.07, y=y*1.07, colour=group, size=value, alpha=0.2)) +
  scale_colour_manual(values= rep( brewer.pal(9,"Paired") , 30)) +
  scale_size_continuous( range = c(0.1,10) ) +
  
  theme_void() +
  theme(
    legend.position="none",
    plot.margin=unit(c(0,0,0,0),"cm"),
  ) +
  expand_limits(x = c(-1.3, 1.3), y = c(-1.3, 1.3))
```


Test2 {.storyboard}
=========================================
```{r}
dataUU <- scores

connect <- dataUU %>% 
  gather(key="to", value="value", -1) %>%
  mutate(to = gsub("\\.", " ",to)) %>%
  na.omit() 


c( as.character(connect$from), as.character(connect$to)) %>%
  as.tibble() %>%
  group_by(value) %>%
  summarize(n=n()) -> valence
colnames(valence ) <- c("name", "n")
#dim(coauth)


mygraph <- graph_from_data_frame( connect, vertices = coauth, directed = FALSE )

com <- walktrap.community(mygraph)
#max(com$membership)

coauth <- coauth %>% 
  mutate( grp = com$membership) %>%
  arrange(grp) %>%
  mutate(name=factor(name, name))


coauth <- coauth %>% 
  filter(grp<16)

connect <- connect %>%
  filter(from %in% coauth$name) %>%
  filter(to %in% coauth$name)


mygraph <- graph_from_data_frame( connect, vertices = coauth, directed = FALSE )


mycolor <- colormap(colormap=colormaps$viridis, nshades=max(coauth$grp))
mycolor <- sample(mycolor, length(mycolor))


ggraph(mygraph, layout="linear") + 
  geom_edge_arc(edge_colour="black", edge_alpha=0.2, edge_width=0.3, fold=TRUE) +
  geom_node_point(aes(size=n, color=as.factor(grp), fill=grp), alpha=0.5) +
  scale_size_continuous(range=c(0.5,8)) +
  scale_color_manual(values=mycolor) +
  geom_node_text(aes(label=name), angle=65, hjust=1, nudge_y = -1.1, size=2.3) +
  theme_void() +
  theme(
    legend.position="none",
    plot.margin=unit(c(0,0,0.4,0), "null"),
    panel.spacing=unit(c(0,0,3.4,0), "null")
  ) +
  expand_limits(x = c(-1.2, 1.2), y = c(-5.6, 1.2)) 
```





